---
title: "Homework 1"
author: Pangsibo Shen
output: github_document
---

# This is my solution to HW1.

```{r}
library(tidyverse)
```

## Problem 1

#### Create a data frame with the specific elements.

```{r create_df}
prob1_df = tibble(samp =  rnorm(10),
  samp_gt_0 = samp >0,
  char_vec = c("a","b","c","d","e","f","g","h","i","j"),
  factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
)

prob1_df
```

#### Take the mean of each variable in my data frame.

```{r mean_pull}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```
#### answer:

I can take the mean of numbers and logical but not character or factor.

```{r try_numeric,results= "hide"}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
#### answer:

I can't convert character into numeric. By converting logical to numeric, TRUE has value of 1 and FALSE has value of 0. For factors, the conversion assigns numeric value to each data point by their levels. 

```{r try_other_conversion}
as.numeric(pull(prob1_df,samp_gt_0))*prob1_df$samp
as.factor(pull(prob1_df,samp_gt_0))*prob1_df$samp
as.numeric(as.factor(pull(prob1_df,samp_gt_0)))*prob1_df$samp
```

## Problem 2

#### install and load penguins dataset
```{r load penguins}
data("penguins", package = "palmerpenguins")
```

#### short description of the penguins dataset

The penguins dataset has *`r nrow(penguins)`* rows and *`r ncol(penguins)`* columns. Column names are *`r names(penguins)`*. There are *`r levels(pull(penguins, species))`* for species and they live on islands like *`r levels(pull(penguins, island))`*. The mean bill depth is *`r mean(pull(penguins, bill_depth_mm), na.rm =TRUE)`* mm. The mean bill length is *`r mean(pull(penguins, bill_length_mm), na.rm =TRUE)`* mm. The mean flipper length is *`r mean(pull(penguins, flipper_length_mm), na.rm =TRUE)`* mm. The mean body mass is *`r mean(pull(penguins, body_mass_g), na.rm =TRUE)`* g. The data was recorded between year *`r range(pull(penguins, year))`*. 

#### scatterplot of bill length vs flipper length and export

```{r scatterplot}
ggplot(penguins,aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)#export the scatterplot
```

